### 2013-12-14 paper/paper.tex
so much hate

\documentclass[letterpaper,12pt]{article}
% define the title
\usepackage{xcolor,graphicx,subfigure}

@@

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}
\usepackage[margin=1.25in]{geometry}

@@

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository using machine-learning techniques. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy. The next section frames this project with the related work of others. Section [CITE] discusses our approach in developing out model including data sources, feature selection, and algorithm development. Section [CITE] discusses the refinement of the model, presents our results, and discusses our methodology for validation of our results. Section [CITE] discusses shortcomings, threats to validity, and future work, and section [CITE] concludes.

@@

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits.  Our work differs from theirs in several ways, namely that their work focuses much more heavily on analysis of committed code, which we generally ignore in favor of the attributes and message of a commit.    
\section{Approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets (Table CITE). The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and ASDFASDFASDFSAD some nuclear reactor thingy. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Kincaid metric for readability [CITE], diction, a unix command line tool, to quantify style (triteness, over-wordiness) [CITE], and Queequeg to test the degree of grammatical correctness [CITE] for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of attributes examined can be found in Table [CITE].

\subsection{Automatically Classifying Past Commits}
To create a classification model from these features, we require a ground truth about whether or not each commit was bug inducing. We used a modified version of the SZZ algorithm from [CITE] to determine the set of commits for each repository that were bug inducing. This technique works by first identifying the set of commits in the repository which are bug fixes. Our modification of the algorithm accomplishes this with an analysis of the commit message looking either for words such as “bug” or “fix” or for strings of numbers and letters that appear to be bug-tracking numbers. After defining this set of bug fix commits, we process each commit individually, identifying sections of source code, called hunks, that the commit altered. For each hunk, we then flag as bug-inducing the most-recent commit before the bug fix commit which altered that hunk of code. This analysis is conducted using a annotation ASDFASDFASF (graph/tree) search [CITE]. Obviously, this heuristic is imperfect; it depends on bug fix commits being atomic and on bugs being discovered and fixed immediately after their introduction. However, as ASDFSDAF et. al showed in [CITE], this technique tends to work well in practice, as their study using actual developers to confirm bugginess found only a 4-5\% rate of false positives. This algorithm works well in practice and serves as a good estimation for which commits are bug inducing, so we adopted it.

\subsection{Machine Learning Algorithms}
With features extracted and a bugginess classification in hand for each commit for our selected repositories, we have the input prepared for constructing, training, and validating a machine-learning algorithm. The method we selected to predict bugginess is an ensemble classifier, or in other words an aggregation of the outputs of several machine-learning algorithms (see Table CITE (listing ML algorithms and their parameters). The tuning of this method involved an iterative process which included selecting the ideal set of features to train and test on, the sizes of both the training and testing datasets, and the machine-learning algorithms and their parameters to serve as initial classifiers. We made sure to include at least one decision tree algorithm as part of our ensemble method due to the extra intuition which can be gained from an examination of the first few splits of its branches. Our prescriptive remarks to future repository committers were largely influenced by the output of these trees.

@@

The simple, obvious solution would be to classify a pull request clean if all commits in it are clean, otherwise buggy.  This seems to be too drastic a measure however, due to these “oops” commits; any method for classifying requests should take into account that buggy commits in a pull request can potentially contain the associated bug fix in the same request.  We propose a variation on the SZZ algorithm to handle this possibility.  All commits are initially given a label using our ensemble classifier.  For a buggy commit in the pull request, we take every hunk from the commit and look forward in time for a clean commit with that hunk.  Finding a hunk in a clean commit would imply that whatever bug originally existed has been fixed.  If all the buggy hunks have corresponding clean hunks later in the pull request, or if the number of unpaired buggy hunks is below some threshold, the pull request is accepted as clean.

@@

\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | }
    \hline

@@

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table {CITE}.  
\begin{table}[h]
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Start Date & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit &Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

@@

 \begin{figure}[h]
\centering
	\includegraphics[width=0.75\textwidth]{images/history}
\caption{Testing and Training Sets}
\label{git_comp}

@@

@@

\begin{figure}[h]
    \centerline{
        \subfigure[Git]{%
            \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_git}
        }%
        \subfigure[Puppet]{%
           \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_puppet}
        }
        \subfigure[Scala]{%
            \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_scala}
        }%
 }
 \caption{Percent Buggy Commits over Time}
\end{figure}

@@

\subsection{Learner Accuracy}

 \begin{figure}[h]
\centering
	\includegraphics[width=1.0\textwidth,height=.7\textwidth]{images/learner_comp}
\caption{Comparison of Feature Results - 1 Year}
\label{git_comp}

@@

As much as we would like it to be otherwise, the 93.3 \% accuracy seen by jedit is more than a little misleading; the jquery test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is true for the majority of message-only feature classifiers; only cyclus and jquery classifiers ever classify any test commits as buggy.  The results from these classifiers are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits.   All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries.

MOAR DATA HERE PLZ SOMETHING WIT RECALL AND PRECISION

@@

 \begin{figure}[h]
\centering
	\includegraphics[width=1.0\textwidth,height=.7\textwidth]{images/time_comp}
\caption{Training Data Size - Message and Attributes}
\label{git_comp}

@@

 \begin{figure}[h]
\centering
	\includegraphics[width=1.0\textwidth]{images/git_comp}
\caption{Training With Git and Scipy - 1 Months, Message and Attribute Data}
\label{git_comp}

@@

\section{Future Work}
More work on heuristic
More work on message representation (NLP)
User history instead of/in addition to commit history
semi supervised learning?
If commits aren’t idiosyncratic to repositories, maybe they are to developers?

>>>>

\documentclass[letterpaper,12pt]{article}
% define the title
\usepackage{subfig}

\usepackage{graphicx}
\usepackage{subfig}
\usepackage{multirow}
\usepackage{array}

@@

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{16cm}
\setlength\epigraphrule{1pt}
\usepackage[margin=1in]{geometry}

@@

In this paper, we discuss our development of a model which attempts to predict the bugginess of commits submitted to a repository using machine-learning techniques. This tool furthers the goal of better directing the testing efforts of repository owners by providing recommendations about which commits are most likely to be buggy. The next section frames this project with the related work of others. Section [CITE] discusses our approach in developing our model including data sources, feature selection, and algorithm development. Section [CITE] discusses the refinement of the model, presents our results, and discusses our methodology for validation of our results. Section [CITE] discusses shortcomings, threats to validity, and future work, and section [CITE] concludes.

@@

Some work has also been done by this group at attempting to use machine learning techniques to predict the bugginess of future commits.  Our work differs from theirs in several ways, namely that their work focuses much more heavily on analysis of committed code, which we generally ignore in favor of the attributes and message of a commit.    
\section{Approach}
\subsection{Mining Git Repositories}
We mined eight open-source repositories hosted on Github.com for features to serve as our testing data sets (Table CITE). The repositories are quite varied; they range in size from around 2000-30000 commits and in age from roughly 3-13 years. The repositories also vary considerably in their goals — they include a programming language, a versioning control system, and a nuclear fuel cycle simulator. We extracted two sets of features about commits from each repository: commit attributes and message attributes. Commit attributes are information about a commit excluding actual analysis of the code or the commit message. Examples of commit attributes we extracted are the number of lines added, the number of lines removed, the contributor, the length of the comment, the day of the week of the commit, and the number of files altered. The commit message attributes we selected are the frequency of words, grammatical correctness, and readability and stylistic metrics of the message. We used the Kincaid metric for readability [CITE], diction, a unix command line tool, to quantify style (triteness, over-wordiness) [CITE], and Queequeg to test the degree of grammatical correctness [CITE] for each commit message. Our analysis of the commit messages assumes they are written in English. A complete list of attributes examined can be found in Table [CITE].

\subsection{Automatically Classifying Past Commits}
To create a classification model from these features, we require a ground truth about whether or not each commit was bug inducing. We used a modified version of the SZZ algorithm from [CITE] to determine the set of commits for each repository that were bug inducing. This technique works by first identifying the set of commits in the repository which are bug fixes. Our modification of the algorithm accomplishes this with an analysis of the commit message looking either for words such as “bug” or “fix” or for strings of numbers and letters that appear to be bug-tracking numbers. After defining this set of bug fix commits, we process each commit individually, identifying sections of source code, called hunks, that the commit altered. For each hunk, we then flag as bug-inducing the most-recent commit before the bug fix commit which altered that hunk of code. This analysis is conducted using an annotation graph search [CITE]. Obviously, this heuristic is imperfect; it depends on bug fix commits being atomic and on bugs being discovered and fixed immediately after their introduction. However, as ASDFSDAF et. al showed in [CITE], this technique tends to work well in practice, as their study using actual developers to confirm bugginess found only a 4-5\% rate of false positives. This algorithm works well in practice and serves as a good estimation for which commits are bug inducing, so we adopted it.

\subsection{Machine Learning Algorithms}
With features extracted and a bugginess classification in hand for each commit for our selected repositories, we have the input prepared for constructing, training, and validating a machine-learning algorithm. After some experimentation with individual classifiers, the method we selected to predict bugginess is an ensemble classifier, which aggregates the outputs of several machine-learning algorithms (see Table CITE (listing ML algorithms and their parameters). Ensemble classifiers generally provide more accurate and consistent results than a single classifier because (assuming the individual classifiers are searching different parts of the hypothesis space) the likelihood of a majority of classifiers being wrong is less likely than a single classifier being incorrect. An added benefit of using an ensemble classifier is it easily allows the user to specify a confidence value for classifying commits as buggy; the more classifiers in agreement, the higher the confidence.  Unless otherwise stated our results take the simple majority of the classifications returned.

 The tuning of this method involved an iterative process which included selecting the ideal set of features to train and test on, the sizes of the training datasets, and the machine-learning algorithms and their parameters to serve as initial classifiers. We made sure to include at least one decision tree algorithm as part of our ensemble method due to the extra intuition which can be gained from an examination of the first few splits of its branches. Our prescriptive remarks to future repository committers were largely influenced by the output of these trees.

@@

The simple, obvious solution would be to classify a pull request clean if all commits in it are clean, otherwise buggy.  This seems to be too drastic a measure however, due to these “oops” commits; any method for classifying requests should take into account that buggy commits in a pull request can potentially contain the associated bug fix in the same request.  We propose a variation on the SZZ algorithm to handle this possibility.  All commits are initially given a label using our ensemble classifier.  For a buggy commit in the pull request, we take every hunk from the commit and look forward in time for a clean commit with that hunk.  Finding a hunk in a clean commit would imply that whatever bug originally existed has been fixed.  If all the buggy hunks have corresponding clean hunks later in the pull request, or if the number of unpaired buggy hunks is below some threshold, the pull request is accepted as clean.  Unfortunately due to time constraints we were not able to test the effectiveness of this method.

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | }
    \hline

@@

To test the effectiveness of our feature selection, we mined features from eight open source repositories.  We attempted to choose projects with different life spans and applications to make our results more generalizable.  The list of projects mined, their number of commits, and the percentage of those commits we found to be buggy are in table {CITE}.  
\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |}
    \hline
    Repository & Start Date & $\#$  Commits & $\#$ Buggy  Commits & \% Buggy \\ \hline
    one     & June 2008   &   8179 & 2744 & 33.6 \\ \hline
    cyclus & March 2010 &  2162 & 1071 & 49.5 \\ \hline
    git        & April 2005    &   28788 & 10682 & 37.1 \\ \hline
    jedit &Sept 1998 &  6890 & 3190 & 46.3 \\ \hline
    jquery     & March 2006   &   5608 & 3074 & 54.8 \\ \hline
    puppet & April 2005 &  12174 & 4812 & 39.5 \\ \hline
    scala     & Feb 2003   &   20398 & 9584 & 47.0 \\ \hline
    scipy & Feb 2001 &  10035 & 3252 & 32.4 \\ \hline        	
    \end{tabular}
\end{center}\caption{Mined Repositories}
\label{tab:repos}
\end{table}

@@

 \begin{figure}
\centering
	\includegraphics[width=0.75\textwidth]{images/history}
\caption{Testing and Training Sets}
\label{git_comp}

@@

	\begin{table}
\begin{center}
    \begin{tabular}{ | c | c | c | c | c |c|}
    \hline

@@

%\begin{figure}
  %  \centerline{
%        \subfigure[Git]{%
%            \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_git}
%        }%
   %     \subfigure[Puppet]{%
      %     \includegraphics[width=0.4\textwidth,height=.3\textwidth]{images/perc_buggy_puppet}
   %     }
   %     \subfigure[Scala]{%
   %         \includegraphics[width=0.4\textwidth,height=.3\textwidth]{}
      %  }%
 %}
% \caption{Percent Buggy Commits over Time}
%\end{figure}

\begin{figure}[H]%
\centering
\subfloat[Git]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_git}}\hfill%
\subfloat[Puppet]{\includegraphics[width=0.5\textwidth]{images/perc_buggy_puppet}}
\caption{Percent Buggy Commits over Time}
\end{figure}

@@

\subsection{Classifier Accuracy}

 \begin{figure}
\centering
	\includegraphics[width=1.0\textwidth,height=.5\textwidth]{images/learner_comp}
\caption{Comparison of Feature Results - 1 Year}
\label{git_comp}

@@

As much as we would like it to be otherwise, the 93.3 \% accuracy seen by jedit is more than a little misleading; the jquery test set is only 6.7\% buggy, and so the jedit classifiers simply guess clean for every instance. This is true for the majority of message-only feature classifiers; only cyclus and jquery classifiers ever classify any test commits as buggy.  The results from these classifiers are still promisingly higher than our baseline, which leads us to believe that our features do have some non-random correlation with clean and buggy commits.   All of our attribute-trained and attribute/message-trained classifiers have non-trivial decision boundaries.  To get a better idea of how well our classifiers actually are at correctly predicting commits as buggy, we examine precision/recall graphs for cyclus, scala (the two repositories with non-trivial decision boundaries) and scipy by varying the ensemble classifier threshold from 0.0\% agreement (always classify buggy) to 100\% agreement.

\begin{figure}[H]%
\centering
\subfloat[Cyclus]{\includegraphics[width=0.5\textwidth]{images/cyclus_pr}}\hfill%
\subfloat[Scala]{\includegraphics[width=0.5\textwidth]{images/scala_pr}}\\
\subfloat[Scipy]{\includegraphics[width=0.5\textwidth]{images/scipy_pr}}\hfill
\subfloat[Cyclus - ROC graph]{\includegraphics[width=0.5\textwidth]{images/cyclus_roc}}\hfill

\caption{Precision Recall Graphs}
\end{figure}

As these figures show, using only comments is better than random.  At the same time, using just comments performs worse in all cases than using attribute data.  Using attribute data performs about as well as training on both attribute and comment features.  This leads us to several conclusions.  First, both sets of attribute and comment features are more predictive than random.  Comparatively, attibute features are a much better approximation of a commit than comment features.  Combining attribute and comment features provide  little additional performance benefit over simply using attributes.

@@

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/time_comp}}\hfill
	\subfloat[Precision Recall Graph]{\includegraphics[width=0.5\textwidth]{images/time_pr}}\hfill

\caption{Training Data Size - Message and Attributes}
\label{git_comp}

@@

 \begin{figure}[h]
\centering
	\subfloat[Accuracy]{\includegraphics[width=0.5\textwidth,height=0.3\textwidth]{images/git_comp}}
	\subfloat[Precision Recall]{\includegraphics[width=.5\textwidth]{images/git_pr}}
\caption{Training With Git and Scipy - 1 Months, Message and Attribute Data}
\label{git_comp}

@@

\section{Future Work}
There are many potential avenues of future work that could stem from this work. One of the most important aspects of a commit that has purposefully been ignored in this work is the committed code itself.  It is possible to investigate lightweight analysis of code changes could provide valuable indications of bugginess without making training our classifier intractable.  Also, we believe looking at commit messages through the lense of more advanced natural language processing techniques could yield additional benefits.

Our results have shown commits are not especially repository specific, but we believe they could potentially be user-specific?  Does it make more sense to have a user-specific classifier that examines the user’s commit history across the repositories they have contributed to than to have a single classifier that predicts labels for potentially many users. Studying this would not require much additional new work to be done beyond mining new repositories and organizing training sets.  If user-specifc commits are in fact better predictors of bugginess, additional work would need to be done to ensure user’s do not cherry-pick their training data to give an overly positive but invalid bias.

Another potential way to approach this problem is through semi-supervised learning.  Rather than attempting to classify all commits as clean or buggy which  requires automatic heuristics, the classifier could simply keep the distribution of commit features stored, some subset of which the user has manually classified as clean and buggy.  The model could then be set up to request labels on past commits that it finds interesting or questionable.
